infer: An R package for tidyverse-friendly statistical inference

### 2021-07-10 figs/paper/paper.Rmd
Update figs/paper/paper.Rmd
"the package" -> "the `infer` package"

`infer` is an R package for randomization-based hypothesis testing, naturalizing an intuitive understanding of statistical inference via a unified and expressive grammar. Four functions provide functionality encompassing a large swath of basic frequentist statistical inference, abstracting away details of specific tests and shifting the focus of the analyst to the observed data and the processes that generated it. Such a grammar lends itself to applications in teaching, data pedagogy research, applied scientific research, and advanced predictive modeling. For one, the principled approach of the package has made it an especially good fit for teaching introductory statistics and data science [@ismay2019statistical; @baumer2020teaching; @cetinkaya2021fresh] and research in data pedagogy [@fergusson2021introducing; @loy2021bringing]. Further, the package has already seen usage in a number of published scientific applications [@mclean2021controlled; @ask2021per; @fallon2021single]. Finally, the package integrates with the greater tidymodels collection of packages, a burgeoning software ecosystem for tidyverse-aligned predictive modeling used across many modern research and industrial applications [@kuhn2020tidymodels]. To date, the package has been downloaded more than 400,000 times.

@@

+ `visualize()` plots the null distribution of test statistics.
     * `shade_p_value()` situates the observed statistic in the null distribution, shading the region as or more extreme.
+ `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and null distribution.

@@

Beyond this, the package offers:

>>>>

`infer` is an R package for randomization-based hypothesis testing, naturalizing an intuitive understanding of statistical inference via a unified and expressive grammar. Four functions provide functionality encompassing a large swath of basic frequentist statistical inference, abstracting away details of specific tests and shifting the focus of the analyst to the observed data and the processes that generated it. Such a grammar lends itself to applications in teaching, data pedagogy research, applied scientific research, and advanced predictive modeling. For one, the principled approach of the `infer` package has made it an especially good fit for teaching introductory statistics and data science [@ismay2019statistical; @baumer2020teaching; @cetinkaya2021fresh] and research in data pedagogy [@fergusson2021introducing; @loy2021bringing]. Further, the package has already seen usage in a number of published scientific applications [@mclean2021controlled; @ask2021per; @fallon2021single]. Finally, the package integrates with the greater tidymodels collection of packages, a burgeoning software ecosystem for tidyverse-aligned predictive modeling used across many modern research and industrial applications [@kuhn2020tidymodels]. To date, the package has been downloaded more than 400,000 times.

@@

+ `visualize()` plots the null distribution of test statistics.
     * `shade_p_value()` situates the observed statistic in the null distribution, shading the region as or more extreme.
+ `get_p_value()` calculates a p-value via the juxtaposition of the test statistic and the null distribution.

@@

Beyond this, the `infer` package offers:
